### 2013-06-26 report/report-1.Rmd
'status' removed from stand variables in report Rmd file.
Gloabl vars removed, var.def and dir.rawData now accessed via function mashrDetail("..")

  vars <- c("location","grouping","growingCondition","status")
  sta <- data[!duplicated(data[,vars]),vars]

@@

printMeta  <-  function(data){
  dataset   <-  as.character(unique(data$dataset))
  openMeta  <-  read.csv(paste0("../",dir.rawData,"/",dataset,"/studyMetadata.csv"), h=TRUE, stringsAsFactors=FALSE)
  openMeta
}

@@

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%var.def$Variable[var.def$Group=="tree"]]
cbind(counts)
```

>>>>

  vars <- c("location","grouping","growingCondition") #,"status")
  sta <- data[!duplicated(data[,vars]),vars]

@@

printMeta  <-  function(data){
  dataset   <-  as.character(unique(data$dataset))
  openMeta  <-  read.csv(paste0("../",mashrDetail("dir.raw"),"/",dataset,"/studyMetadata.csv"), h=TRUE, stringsAsFactors=FALSE)
  openMeta
}

@@

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%mashrDetail("var.def")$Variable[mashrDetail("var.def")$Group=="tree"]]
cbind(counts)
```
